Medauo Amicus Brief Models

### 2022-04-22 modeling/amicus_type/medauo.Rmd
close #27

library(tidyverse)
library(lme4)
library(boxr)
box_auth()
```

@@

```{r}
data <- box_read("948366662469") %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

@@

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
data %>% head(1) %>% select(case:justicefem)
```

@@

Remove cols where all values are NA. Not sure if we will do this or not in models. Technically, we should...?

@@

* 0.5: compulsory_motherhood, morality&relig, protesters
* .1: undue burden

@@

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_abortion_different,
              family = binomial, data = data_scale,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_physician,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

amicus_only <- "948366662469"
full_cases <- "948832669583"
```

@@

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

@@

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

@@

Remove cols where all values are NA. Not sure if we will do this or not in models.

@@

* 0:
* 0.01
* 0.05:
* .1:

@@

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                medauo_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
